A Methodology and Implementation of Automated Emissions Harmonization for Use in Integrated Assessment Models

### 2018-02-06 correspondance/revision1_letter/letter.tex
adjust slight wording and spacing of letter

\begin{letter}{
    Professor S. Reis\\
    Editor, Environmental Modelling \& Software\\
    \hfill\break
    Professor D.P. Ames\\
    Editor-in-Chief, Environmental Modelling \& Software\\
  }

@@

After revision, we believe that the manuscript has been improved over the
initially submitted draft. The authors would like to thank the reviewers for
their constructive comments and suggestions as well as for their time taken to
review our article. We would also again like to thank you again for your
consideration of this work.

\closing{
Warm Regards,

Matthew Gidden, Ph.D.
}

>>>>

\begin{letter}{
    Professor S. Reis\\
    Editor, Environmental Modelling \& Software\\
    \hfill\break
    Professor D.P. Ames\\
    Editor-in-Chief, Environmental Modelling \& Software
    \hfill\break
  }

@@

The authors believe that the manuscript has been improved over the initially
submitted draft. We would like to thank the reviewers for their constructive
comments and suggestions as well as for their time taken to review our
article. We would also again like to thank you again for your consideration of
this work.

\closing{
  \hfill\break
  \hfill\break
  Warm Regards,\\
  \hfill\break
  Matthew Gidden, Ph.D.
}
